---
format:
  revealjs:
    width: 1280
    height: 720
    transition: none
    include-after-body:
      - "all-the-js-code.html"
pagetitle: GL Transitions Demo
echo: false
code-line-numbers: false
---

## PuzzleRight {data-gl-transition="PuzzleRight"}

```{r}
library(ggplot2)
ggplot(mpg, aes(displ, hwy, color = class)) +
  geom_point(size = 3) +
  labs(title = "Engine displacement vs highway mpg")
```

## crosswarp {data-gl-transition="crosswarp"}

```{r}
ggplot(diamonds, aes(cut, fill = cut)) +
  geom_bar() +
  labs(title = "Diamond counts by cut")
```

## burn0 {data-gl-transition="burn0"}

```{r}
ggplot(faithfuld, aes(eruptions, waiting)) +
  geom_tile(aes(fill = density)) +
  scale_fill_viridis_c() +
  labs(title = "Old Faithful eruption density")
```

## StarWipe {data-gl-transition="StarWipe"}

```{r}
ggplot(mpg, aes(hwy)) +
  geom_histogram(bins = 30, fill = "steelblue", color = "white") +
  labs(title = "Distribution of highway mpg")
```

## Color background {data-gl-transition="crosswarp" background-color="#4a90d9"}

This slide has a solid **blue** background color.

## Gradient background {data-gl-transition="burn0" background-color="#e8a838"}

This slide has a solid **orange** background color.

## Dark background with plot {data-gl-transition="windowslice" background-color="#1a1a2e"}

```{r}
ggplot(mpg, aes(displ, hwy)) +
  geom_point(color = "#e8a838", size = 2, alpha = 0.8) +
  theme_dark() +
  labs(title = "Dark theme plot on dark slide")
```

## Image background {data-gl-transition="zoomInOut" background-image="https://images.unsplash.com/photo-1506905925346-21bda4d32df4?w=1280&h=720&fit=crop" background-opacity="0.4"}

Text overlaid on an **image background**.

## Back to white {data-gl-transition="wipeRight"}

Plain slide after all the backgrounds — checking the transition lands cleanly.
